\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2015-05-27 Paper.tex
10 pages

\begin{wrapfigure}{l}{\textwidth}
\vspace{-0pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.70\textwidth]{assets/final/Architecture}
    } 
\vspace{-6pt}
  \caption{Architecture Diagram}
  \label{fig:architecture}
\vspace{12pt}
  \end{center}
\end{wrapfigure}

@@

With the OMDoc framework and its tools it is possible to write down course notes or other documents in \textbf{S}emantically enhanced \TeX / \LaTeX\ (\stex). The Local MathHub Tool (lmh) uses these to create, among other things, PDF slides, XHTML slides, and relational information. To help Annie, let us use a document that explains the Pythagorean theorem and related topics. The files that lmh creates, along with the \stex -files will be used as input in the next steps. For the implementation of  \sys Java was used. It would have been possible to choose other programming languages, however, using Java, we end up with platform-independent code.\\

@@

These concepts can be adapted to the situation of teaching mathematics or computer science to students in a class. In general we will call the information that the speaker is passing on to the addressees/students \textit{course-new}. Since we are in the setting of a university course, the \textit{course-new} information will generally depend on information that is \textit{course-old}. We will additionally introduce a third modus for information called \textit{course-ancient}. This covers the situation where the addressee has difficulties following the speaker since the \textit{course-new} information depends on \textit{course-old} information that might be 'too old' to be easily remembered, i.e. \textit{course-ancient}.\\

@@

As described in \autoref{sec:TowardsAMoreEffectivePresentationFormat}, lmh outputs information about dependencies of topics.The system \sys parses this relational data and retrieves the dependencies of the topics which are visualized for Annie's example in \autoref{fig:depGraphPythagoreanFull}. Dependencies give us the \textit{course-ancient} information, as dependencies intuitively link to information obtained longer ago.\\

@@

\begin{wrapfigure}{c}{1\textwidth}
\vspace{-16pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.87\textwidth]{assets/final/fullPresentation2}
    } 
\vspace{-7pt}
  \caption{Visualization of Dependencies}
  \label{fig:visualDependency}
\vspace{-15pt}
  \end{center}
\end{wrapfigure}

@@

\begin{wrapfigure}{l}{0.57\textwidth}
\vspace{-26pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.55\textwidth]{assets/final/60degree}
    } 
\vspace{-5pt}
  \caption [Caption for LOF]{Visualization of Dependencies and Levels at 60\degree\ \footnotemark}
  \label{fig:visualDependencyDegree}
\vspace{-24pt}
  \end{center}
\end{wrapfigure}

@@

One might think that this is similar to a PowerPoint presentation, since PowerPoint offers similar animations to switch slides. The important addition is more obvious when regarding the presentation from a bird's eye perspective by looking at the overview in \autoref{fig:visualDependency} or \autoref{fig:visualDependencyDegree}. The value in these presentations is that through these overviews, dependencies become identifiable. More importantly this means that for Annie, dependencies become accessible and allow her to go on small guided tours or small excursions into \textit{course-ancient} topics giving her the flexibility to choose her own path while going through the presentation.

@@

In this research project we set out to help Annie understand the Pythagorean theorem. Her problem was that she did not know about some of the dependent information, i.e. right angles, and since there was no easy way to access this information she could not understand the topic fully. To help her, we created a system \sys that parses the documents that the instructor wrote and created a relational presentation out of it.\\

@@

The benefits are not just for Annie when she is going through the presentation on her own though, Annie's teacher now has a tool that allows him to use his normal lecture material in a more interactive way. Thus when the teacher realizes that the students need to revise previous material, the teacher can seamlessly go to that material and provide them with a good learning experience. This facilitates knowledge transfer and allows for a more engaging and interactive education.\\

In the future, I believe that this research could be adopted in more fields, transforming education into something that allows individuals to learn the way that is best for them. In the introduction, I introduced the metaphor of hiking up a mountain which can be done in different ways. The type of presentations this research built allows for a lot of different paths to reach a learning goal. The flexibility that comes with these presentations is undoubtedly preferable to traditional presentations as it offers clear benefits in allowing to effortlessly change the path of the presentation at any point.\\

@@

\ednote{There some argued that the linking of learning materials is useful for knowledge transfer and that especially mathematics is a field that could profit from guided tours through topics as a way of learning topics according to users' individual knowledge bases.}

\ednote{These digressions are the added value that allow flexibility in these new presentation and transform the traditional presentations from linear presentations to relational presentations.}

>>>>

\begin{wrapfigure}{l}{\textwidth}
\vspace{-22pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.55\textwidth]{assets/final/Architecture}
    } 
\vspace{-6pt}
  \caption{Architecture Diagram}
  \label{fig:architecture}
\vspace{0pt}
  \end{center}
\end{wrapfigure}

@@

With the OMDoc framework and its tools it is possible to write down course notes or other documents in \textbf{S}emantically enhanced \TeX / \LaTeX\ (\stex). The Local MathHub Tool (lmh) uses these to create, among other things, PDF slides, XHTML slides, and relational information. To help Annie, let us use a document that explains the Pythagorean theorem and related topics. The files that lmh creates, along with the \stex -files will be used as input in the next steps. For the implementation of  \sys Java was used.\\

@@

These concepts can be adapted to the situation of teaching mathematics or computer science to students in a class. In general we will call the information that the speaker is passing on to the addressees/students \textit{course-new}. Since we are in a classroom setting, the \textit{course-new} information will generally depend on information that is \textit{course-old}. We will additionally introduce a third modus for information called \textit{course-ancient}. This covers the situation where the addressee has difficulties following the speaker since the \textit{course-new} information depends on \textit{course-old} information that might be 'too old' to be easily remembered, i.e. \textit{course-ancient}.\\

@@

As described in \autoref{sec:TowardsAMoreEffectivePresentationFormat}, lmh outputs information about dependencies of topics. \sys parses this relational data and retrieves the dependencies of the topics which are visualized for Annie's example in \autoref{fig:depGraphPythagoreanFull}. Dependencies give us the \textit{course-ancient} information, as dependencies intuitively link to information obtained longer ago.\\

@@

\begin{wrapfigure}{c}{1\textwidth}
\vspace{-16pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.67\textwidth]{assets/final/fullPresentation2}
    } 
\vspace{-7pt}
  \caption{Visualization of Dependencies}
  \label{fig:visualDependency}
\vspace{-15pt}
  \end{center}
\end{wrapfigure}

@@

\begin{wrapfigure}{l}{0.42\textwidth}
\vspace{-20pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.4\textwidth]{assets/final/60degree}
    } 
\vspace{-15pt}
  \caption [Caption for LOF]{Visualization of Dependencies and Levels at 60\degree\ \footnotemark}
  \label{fig:visualDependencyDegree}
\vspace{-24pt}
  \end{center}
\end{wrapfigure}

@@

One might think that this is similar to a PowerPoint presentation, since PowerPoint offers similar animations to switch slides. The important addition is more obvious when regarding the presentation from a bird's eye perspective by looking at the overview in \autoref{fig:visualDependency} or \autoref{fig:visualDependencyDegree}. The value in these presentations is that dependencies become identifiable. More importantly this means that for Annie, dependencies become accessible and allow her to go on small guided tours or small excursions into \textit{course-ancient} topics giving her the flexibility to choose her own path while going through the presentation.

@@

We set out to help Annie understand the Pythagorean theorem. Her problem was that she did not know about some of the dependent information, i.e. right angles, and since there was no easy way to access this information she could not understand the topic fully. To help her, we created a system \sys that parses the documents that the instructor wrote and created a relational presentation out of it.\\

@@

The benefits are not just for Annie when she is going through the presentation on her own though, Annie's teacher now has a tool that allows him to use his normal lecture material in a more interactive way. Thus when the teacher realizes that the students need to revise previous material, the teacher can seamlessly go to that material and provide them with a good learning experience. These digressions are the added value that allow flexibility in these new presentation and transform the traditional presentations from linear presentations to relational presentations. Overall this facilitates knowledge transfer and allows for a more engaging and interactive education.\\

Linking learning materials is useful for knowledge transfer and especially mathematics is a field that could profit from guided tours through topics as a way of learning topics according to users' individual knowledge bases. In future, I believe that this research could be adopted in more fields, transforming education into something that allows individuals to learn the way that is best for them. In the introduction, I introduced the metaphor of hiking up a mountain which can be done in different ways. The type of presentations this research built allows for a lot of different paths to reaching a learning goal. The flexibility that comes with these presentations is undoubtedly preferable to traditional presentations as it offers clear benefits in allowing to effortlessly change the path of the presentation at any point.\\

@@
